---
title: "Project for Theoretical Statistics"
author: "Jung-Han Wang"
date: "September 8, 2015"
output: pdf_document
---

In today class, we have an optional project for Theoretical Statistics I.

In the lecture, Professor Zhang mentioned that the selection can be categorized into four settings.

|         | without replacement| with replacement|
|--------:|-------------------:|----------------:|
|  Ordered|$\dfrac{n!}{(n-r)!}$| $n^{r}$           |
|Unordered| ${{n}\choose{r}}$  | ${{n+r-1}\choose{r}}$ |

##Variable Explanation

- Variable _replace_, _ordered_, are binary variables with value 0 or 1.
- Variable _ticket_ is the number of lottery bought.
- Variable _n_ is all the numbers that you can choose.
- Variable _c_ is the number of selected for any subset.

I found out that the factorial function in base R use gamma approximation.  When the value is too large the result will be biased.  In this case, I created a fatorial function called _myFactorial_

The R Code starts here:
```{r}
rm(list=ls())   ##Clear memory space

## Create Function to calculate Factorial 
myFactorial <- function(x) {
    if (x == 0)
      {return(1)}
  return(x*myFactorial(x-1))
}

## Function to determine integer
check.integer <- function(x) {
    x == round(x)
}

lottery<-function(replace=0,ordered=0,ticket=1,n=53,r=6){
  stopifnot(replace==0|replace==1)  ##Stop if replace is not a binary variable
  stopifnot(ordered==0|ordered==1)  ##Stop if ordered is not a binary variable
  stopifnot(check.integer(ticket))  ##Stop if ticket is not an integer
  stopifnot(ticket>0)               ##Stop if ticket is less than 1
  stopifnot(check.integer(n))       ##Stop if n is not an integer
  stopifnot(check.integer(r))       ##Stop if r is not an integer
  stopifnot((n-r)>0)                ##Make sure n greater than r
  
  #Categorize them into four categories
  if (replace==0 && ordered==1){type=1}
  else if (replace==1 && ordered==1){type=2}
  else if (replace==0 && ordered==0){type=3}
  else if (replace==1 && ordered==0){type=4}

  #Calculate for type=1 which is without replacement but ordered
  if (type==1){
    event<-myFactorial(n)/myFactorial(n-r)
  }
  #Calculate for type=2 which is with replacement and ordered
  else if (type==2){
    event<-(n)^(r)
  }
  #Calculate for type=3 which is without replacement nor unordered
  else if (type==3){
    event<-(myFactorial(n))/(myFactorial(r)*myFactorial(n-r))
  }
  #Calculate for type=2 which is with replacement but unorder
  else if (type==4){
    event<-(myFactorial(n+r-1))/(myFactorial(r)*myFactorial(n-1))
  }
  
  ##Calculate winning rate
  winRate<-(1/event)*ticket
  
  return(cat(c(paste0("Your chance of winning the lottery is ",winRate),
       paste0("The number of outcomes is ",event)
       ),sep="\n"))
}
```

##Example1

```{r}
lottery(replace=0,ordered=0,ticket=1,n=54,r=7)
```

##Example2

```{r}
lottery(replace=1,ordered=0,ticket=2,n=35,r=5)
```
